### 2019-04-22 Manuscript/Manuscript.tex
Updates from Overleaf

We use 15\textdegree~S to 15\textdegree~N as the definition of the tropical rain belt, as those latitudes approximately correspond with a sharp increase in zonal mean precipitation to values greater than 1.0~m/yr in modern climatalogical data \citep{Kalnay1996a}. Other parameters that could be used to define the tropical rain belt are runoff and evaporation minus precipitation (E--P). In modern climatological data, runoff sharply increases to values above 0.6~kg/m$^{2}$ between approximately 10 and 20\textdegree\xspace, and E--P sharply decreases to values below 1.5~kg/m$^{2}$/day between approximately 10 and 15\textdegree. Given that it is unclear as to which of these parameters correlates most strongly with long term weathering rates in natural environments, we also tested the sensitivity of our results to the assumed width of the tropical rain belt by performing the tropical LIP area calculations with tropical rain belt widths of $\pm$10\textdegree\xspace and $\pm$20\textdegree. Testing different tropical rain belt widths also has the indirect effect of accounting for uncertainties in the paleolatitude of LIPs in the paleogeographic model. We find that the $\pm$10\textdegree\xspace and $\pm$20\textdegree\xspace tropical rain belts yield similar results to that defined as $\pm$15\textdegree\xspace (Table \ref{tab:stats}).

@@

>>>>

We use 15\textdegree~S to 15\textdegree~N as the definition of the tropical rain belt, as those latitudes approximately correspond with a sharp increase in zonal mean precipitation to values greater than 1.0~m/yr in modern climatalogical data \citep{Kalnay1996a}. Other parameters that could be used to define the tropical rain belt are runoff and evaporation minus precipitation (E--P). In modern climatological data, runoff sharply increases to values above 0.6~kg/m$^{2}$ between approximately 10 and 20\textdegree\xspace \citep{Kalnay1996a}, and E--P sharply decreases to values below 1.5~kg/m$^{2}$/day between approximately 10 and 15\textdegree \citep{Trenberth2011a}. Given that it is unclear as to which of these parameters correlates most strongly with long term weathering rates in natural environments, we also tested the sensitivity of our results to the assumed width of the tropical rain belt by performing the tropical LIP area calculations with tropical rain belt widths of $\pm$10\textdegree\xspace and $\pm$20\textdegree. Testing different tropical rain belt widths also has the indirect effect of accounting for uncertainties in the paleolatitude of LIPs in the paleogeographic model. We find that the $\pm$10\textdegree\xspace and $\pm$20\textdegree\xspace tropical rain belts yield similar results to that defined as $\pm$15\textdegree\xspace (Table \ref{tab:stats}).

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.6\textwidth]{Manuscript/Figures/Climatology.pdf}
	\caption{Zonally averaged modern climatological data from \citet{Kalnay1996a} and \citet{Trenberth2011a} used to define the tropical rain belt. Precipitation and evaporation minus precipitation data are from land and ocean, whereas runoff data are from land only. Note that all of these metrics increase/decrease sharply between 10 and 20\textdegree\xspace.}
	\label{fig:Climatology}
\end{center}
\end{figure}
